### 2023-03-17 main.tex
Density
Fixed

\newcommand{\N}{\mathbf{N}}
\newcommand{\twoj}{\nu}

@@

\mu_{rev}=\bigotimes_{x\in V}\mu_{rev}^{x}

@@

 \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)\quad \text{where}\quad p_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}

@@

\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{k=1}^{N}n_{k}^{x}!}\prod_{k=1}^{N}p_{k}^{n_{k}^{x}}

@@

	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\,\right)

@@

\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}

@@

\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}|\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
	 \otimes(\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle

@@

\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}||q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}|=\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}

@@

 \textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing as a symmetry {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}

@@

@@

H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}^{x}\right)

@@

\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

&H_{x,y}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}-E_{kk}\right)

@@

&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}

@@

\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}

@@

     &H_{x,y}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}-E_{kk}^{x}\right)   

>>>>

\newcommand{\N}{\mathbf{N}}
\newcommand{\twoj}{\nu}
\allowdisplaybreaks

@@

\mu_{rev}=\bigtimes_{x\in V}\mu_{rev}^{x}

@@

 \mu^{x}_{rev}\sim \text{Multinomial}\left(\twoj,\rho_{1},\ldots,\rho_{N}\right)\quad \text{where}\quad \rho_{k}=\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}

@@

\mu_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{k=1}^{N}n_{k}^{x}!}\prod_{k=1}^{N}\rho_{k}^{n_{k}^{x}}

@@

	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(2j-\sum_{k=2}^{N}r_{k}^{x})!}{\nu!}\prod_{k=2}^{N}\frac{n_{k}^{x}!}{(n_{k}^{x}-r_{k}^{x})!}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\,\right)
where we denote the \textit{density} of the species $k\in \{2,\ldots,N\}$ at the reservoir connected with the site $x\in V$  by 
\rho_{k}^{x}:=\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}

@@

\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{\sum_{x\in V}r_{k}^{x}+\sum_{x\in V}m_{k}^{\widehat{x}}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}

@@

\dd=\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\&=\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{12}^{x}+\ldots+E_{1N}^{x}}))^{T}R_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|
	 \\&|r_{1}^{x},\ldots,r_{N}^{x}\rangle_{x} \otimes |q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle

@@

\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}||q_{2}^{\widehat{x}},\ldots,q_{N}^{\widehat{x}}\rangle=\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}

@@

 \textbf{Remark}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $k\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{k}$ is lower or equal than the number of original particles $n_{k}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}

@@

\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}^{x}\right)

@@

H_{x}^{T}R_{x}\exp{(E^{x})}=R_{x}\exp{(E^{x})}\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}^{x}\right)

@@

\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

&H_{x,y}^{T}d_{x}\otimes\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left(\rho_{k}^{x}E_{1k}^{x}-E_{kk}\right)

@@

&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}E_{1k}^{x}
\\=&\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}+1}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}}+1,\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}

@@

\sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{k}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|(a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}

@@

     &H_{x,y}^{T}d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|

@@

d_{x}\otimes \sum_{m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\rho_{k}^{x}\right)^{m_{k}^{\widehat{x}}}\langle m_{2}^{\widehat{x}},\ldots,m_{N}^{\widehat{x}}|\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=1}^{N}\left((a^{\dagger})_{k}^{\widehat{x}}E_{1k}^{x}-E_{kk}^{x}\right)   
